---
title: "Introduction to StatComp20021"
author: "Chi Sun"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to StatComp20021}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Overview

__StatComp20021__ is a simple R package developed to verify the theorem that the empirical log likelihood of the mean of independent random two-dimension vectors with common distribution converges to the chi-square distribution with 2 degree.
The method which supports the independence of the sample is realized by bootstrap.And the comparison will be shown in qqplot.


## calculate the empirical log likelihood of the mean of the original two-dimensional sample using R.
The first step is to design an algorithm to calculate the empirical log likelihood of the mean in the original two-dimensional sample using R.According to the book,Empirical Likelihood by Art B.Owen,there is an easier method to simplify the complex formula for calculating the empirical log likelihood of the mean.The R code for the trick is as follows.
```{r,eval=FALSE}
f <- function(x,y,xbar,ybar) {
  m1<-matrix(c(var(x),cov(x,y),cov(x,y),var(y)),2,2)
  m2<-matrix(c(mean(x)-xbar,mean(y)-xbar),2,1)
  m<-t(m2)%*%ginv(m1)%*%m2
  return(m)
}
```
In the above R code,parameter x,y respectively means the components of the bootstap two-dimension samples.Parameter xbar,ybar means the mean of the original sample.In general,m1 is a matrix with full ranks,hence the result degree of the convergent chi-square distribution is equivalent to the dimensions and "solve" function is enough for use. 

## qqplot for comparison and vertification
The qqplot is a very useful and efficient tool for comparison and vertification in R.After obtaining the empirical log likelihood values of the mean in the original two-dimensional sample by bootstrap method,it is natural to compare them with the random numbers produced by "rchisq".Here is an example.
```{r,eval=TRUE}
library(MASS)
f <- function(x,y,xbar,ybar) {
  m1<-matrix(c(var(x),cov(x,y),cov(x,y),var(y)),2,2)
  m2<-matrix(c(mean(x)-xbar,mean(y)-xbar),2,1)
  m<-t(m2)%*%ginv(m1)%*%m2
  return(m)
}
dqqplot<-function(data,B){
  n<-nrow(data)
  m<-as.matrix(data)
  xbar<-mean(m[,1]);ybar<-mean(m[,2])
  y<- numeric(B)
  set.seed(123)
  for (b in 1:B){
    i <- sample(1:n, size = n, replace = TRUE)
    xb<-m[i,1];yb<-m[i,2]
    y[b]<-n*f(xb,yb,xbar,ybar)
  }
  x<-rchisq(B,2)
  qqplot(x,y)
  abline(0,1,col=2)
}
data<-matrix(c(7,13,14,6,14,1,4,8,7,3,14,5,10,11,6,15,13,5,7,14),ncol=2)
B<-1000
dqqplot(data,B)
```
  
Shown is a qqplot of 1000 bootstrap resampled values of the empirical log likelihood of the mean of the ducks data in the book,versus chi-square quantiles with 2 degree.The solid reference line is the 45° line.The results show that the points fit the line well. 
